\pdftitle

### 2017-05-16 maxNt.tex
worked on Intro

Recent advances in electrophysiological recordings allow to
 study the activity of large population of neurons 
in relation to stimuli and bahavioral tasks [\cite]. Huge amount of parallel
 recordings from hundreds of neurons, available today, is accompanied by
 the statistical challenges to be employed for shedding light on the mechanism behind neuronal coding. 
The principle of \me\ was proposed as a way to overcome these challenges by constructing a full description of the 
neuronal firing patterns. The \me\ method exploits only first and second
order statistics of the observed data and construct a least structured or
a \enquote{maximally noncommital} probability distribution of firing patterns [\cite].

Using the pairwise \me\ models many studies strived for answering 
 questions such as, which level of interaction (pairwise or higher-order) between neurons
 is suffiecient to explain the observed experimental data [\cite]? Or how collective behavior
 of neurons can be related to stimuli or behavioral tasks [\cite]?

Here we show that there is a
contradiction in applying \me\ to the observed data \enquote{representative random sample}
of neurons to generate a \enquote{maximally noncommital} distribution for
that sample.

>>>>

Recent advances in electrophysiological techniques allow to
record from large population of neurons [\cite]. The recorded neurons
are usually picked out according to an unknown process, and from their
observation we expect to learn something about all other neurons in the
same brain area. That is, they are assumed to be a
\enquote{representative random sample} of the neurons in that area.

Huge amount of parallel recordings from hundreds of neurons,
available today, is accompanied by the statistical challenges
to be employed for shedding light on the mechanism behind neuronal coding. 
The principle of \me\ was proposed as a way to overcome these challenges by
constructing a full description of the 
neuronal firing patterns. The \me\ method employs only first and second
order statistics of the representative random sample to construct 
a \enquote{maximally noncommittal} \cite{jaynes1963} 
probability distribution of the firing patterns [\cite].

Using the pairwise \me\ models many studies strived for answering 
 questions such as, which level of interaction (pairwise or higher-order) between neurons
 is suffiecient to explain the observed experimental data [\cite]? Or how collective behavior
 of neurons can be related to stimuli or behavioral tasks [\cite]? add more **

Here we show that there is a
contradiction in applying \me\ to the representative random sample
of neurons to generate a maximally noncommital distribution for
that sample.
